On the minimum leaf conductance: its role in models of plant water use, and ecological and environmental controls

### 2018-01-31 manuscript.Rmd
LP in ackno
updated sureau figure

\
**Figure 5**. Simulations with the *Sureau* model demonstrating the effect of g~min~ on desiccation tolerance of plants. The *Sureau* model simulates water transport in the soil-plant-atmosphere continuum, and includes a detailed representation of capacitance in stem and leaf tissues. (a) Soil relative extractable water (REW; 1 = field capacity, 0 = permanent wilting point) for the two simulations, using a minimum conductance (g~min~) of 1.6 or 3.3 mmol m^-2^ s^-1^ - all other parameters were equal. (b) Water potential in the soil and leaf as the dry-down progresses. Note the brief increase in soil water potential around days 40 - 70; this represents water released from stem cavitation. (c) Progression of percent loss conductivity (PLC) of the xylem. If we assume that plant mortality occurs at a PLC of 88%, the plants with the low g~min~ lasted 15 days longer.

@@

\
It is however an open question on how g~min~ should be parameterized for different species, as we found both large variation between species that could not be explained by traits, and remarkable plasticity to growing conditions. Perhaps this plasticity is the reason that g~min~ did not vary predictably between species. We conclude as a result that g~min~ is not a "trait" in the sense that it can be meaningfully summarized for a given species, but has to be linked to growing conditions. Future studies should compare g~min~ on many species grown in the same conditions to better understand the adaptive value of the minimum water loss rate of leaves.

>>>>

\
**Figure 5**. Simulations with the *Sureau* model demonstrating the effect of g~min~ on desiccation tolerance of plants. The *Sureau* model simulates water transport in the soil-plant-atmosphere continuum, and includes a detailed representation of capacitance in stem and leaf tissues. (a) Soil relative extractable water (REW; 1 = field capacity, 0 = permanent wilting point) for the two simulations, using a minimum conductance (g~min~) of 2 or 4 mmol m^-2^ s^-1^ - all other parameters were equal. (b) Water potential in the soil and leaf as the dry-down progresses. (c) Progression of percent loss conductivity (PLC) of the xylem. Dashed line is at a PLC of 88%, indicating possible mortality.

@@

\
It is however an open question on how g~min~ should be parameterized for different species, as we found both large variation between species that could not be explained by traits, and remarkable plasticity to growing conditions. Perhaps this plasticity is the reason that g~min~ did not vary predictably between species. Future studies should compare g~min~ on many species grown in the same conditions to better understand the adaptive value of the minimum water loss rate of leaves.

# Acknowledgments

This work was made possible by the ARC Linkage Project LP140100232.
